% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={High Level Topics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{High Level Topics}
\author{}
\date{}

\begin{document}
\maketitle

Regarding the DMLD:

\begin{itemize}
\tightlist
\item
  Overview of the B2B, B2B2C, and B2C configurations.
\item
  What level of customization is available for branding the platform to
  fit our company's identity?
\item
  Can customer\textquotesingle s manage and view their service (like
  router config/utilization) through this platform\textquotesingle s
  connections to the OSS?
\item
  What level of customization is available for modifying the
  platform\textquotesingle s modules to our specific needs? Could we add
  additional components, and, if so, what framework was used to build
  it?
\item
  What APIs are available for integrating the DMLD platform with
  existing systems within the Tecnotree solution and external (e.g.,
  ERP, CRM, Self Hosted AI Chatbots)
\item
  What security protocols and measures are implemented to protect
  sensitive customer data?
\item
  Is there built-in fraud protection, whether it be within this platform
  or somewhere else?
\item
  What are the benchmarks for processing times and uptime?
\item
  How does the platform scale to support increasing volumes of
  transactions and users (deployment infra)?
\item
  Can we go over data analytics and reporting for this platform?
\item
  How does this solution fit within the deployment models discussed in
  the previous call?
\item
  Finally, from a purely technical perspective:

  \begin{itemize}
  \tightlist
  \item
    Can you help me understand how you represent the different Objects
    that interact with this platform within your systems?
  \item
    What would the DTO for an external module accessing this platform
    look like, and how flexible are these DTOs in handling additional
    custom fields or business logic?
  \item
    How do you handle user authentication and login flows within the
    platform? Is it password-based only, or does the platform support
    OAuth or other social login methods?
  \item
    How do you manage the user sign-up process and capture the necessary
    data? Is it within this platform or somewhere else? And, can we
    create new users via API?
  \item
    How do you handle account deletion from both a user experience and
    compliance perspective?
  \item
    How do you handle session management, especially for long-running
    sessions? Are there token-based mechanisms (e.g., JWTs) in place for
    session handling, and how are these tokens managed for security
    (e.g., expiration, refresh tokens)?
  \item
    Can you elaborate on how the platform interacts with external
    modules via APIs? What kind of request and response structure do you
    follow, and what authentication mechanisms are in place for secure
    API access?
  \end{itemize}
\end{itemize}

Regarding the DOM:

\begin{itemize}
\tightlist
\item
  What are the core functionalities and how does the DOM system
  integrate with the broader ecosystem?
\item
  How customizable is the user interface for both internal users (e.g.,
  customer service reps, admin) and external customers?
\item
  Are external customers (e.g. Online Potential Customers) supposed to
  interact with this system, or \textbf{can/do} we communicate with the
  order manager through API to achieve this end?
\item
  How does it handle order orchestration and fulfillment?
\item
  Can we go through an example order workflow?
\item
  What integration capabilities are provided to interact with existing
  systems (e.g., CRM, billing, fulfillment systems), and particularly,
  payment processing (innate handling of Apple/Google Pay + PayPal or de
  we need a payment processor)?
\item
  How does this solution connect with the DMLD? I am assuming that after
  placing an order we instantiate the new user and forward to the DMLD.
\item
  The same security compliance, scalability, analytics/reporting,
  performance benchmarks, and deployment questions as above... as
  applicable.
\item
  For technical questions, also very similar to above...
  order/customers/product representation + auth
\end{itemize}

Finally, and this is much more general:

\begin{enumerate}
\tightlist
\item
  How do you handle multi-language needs and accessibility in all your
  solutions?
\item
  Can you give us a run-through of the Digital Architecture presented in
  slide 8 of the Digital BSS Presentation shared on August 21st?
\item
  Regarding your standards for all solutions, it is my belief that
  you\textquotesingle ve adopted TM Forum\textquotesingle s open APIs
  within all areas of your system. Any additional literature you can
  provide about how you conform with these standards would be
  appreciated. If the technical questions are beyond the scope,
  referring us to documentation and standards works for me.
\end{enumerate}

\end{document}
